Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM

### 2011-02-18 results.tex
Length scale study

The solutions to the PNP problem exhibit a specific behavior that was 
described above. In order to find the best adaptive method to deal with 
this type of problems, we performed numerous computations using all 
adaptivity modes in both the single-mesh and multi-mesh regimes.
In the numerical experiments we paid attention to the 
relative error, cumulative CPU time, and problem size 
in terms of number of degrees of freedom (DOF) in each 
time step. The scaled variables $c$
and $\varphi$ and the unscaled time $t$ are used to present the solutions.

@@

>>>>

The solutions to the PNP problem exhibit a specific behavior that was 
described above. In order to find the best adaptive method to deal with 
this type of problems, we performed numerous computations using all 
adaptivity modes in both the single-mesh and multi-mesh regimes.
In the numerical experiments we paid attention to the 
relative error, cumulative CPU time, and problem size 
in terms of number of degrees of freedom (DOF) in each 
time step. The scaled variables $c$
and $\varphi$ and the unscaled time $t$ are used to present the solutions.
The simulations were performed with physical time step of $0.05$~s and
the final time of $3.0$~s was chosen as it is close to the time
scaling constant~$\tau$.

@@

\subsection{Length scale study}

The Debye length $\lambda_D$ is the screening length in the electrolyte
solutions. Its numerical value shows the
thickness of the layer in the vicinity of the boundaries $\partial\Omega_1$ 
and $\partial\Omega_2$  where $c \neq 1$.
In all the previous simulations, the Debye screening length was determined by  the constants in
Table~\ref{Table:used-constants} and Eq.~\ref{eq:debye}: $\lambda_D=XXX$. It is known that computation gets increasingly
difficult when reducing the value of $\lambda_D$.
It was our interest to see how small screening lengths can Hermes HP\_ANISO automatic
adaptivity handle. The parameter $\varepsilon$ was varied as follows:
$$\varepsilon_n=\varepsilon\times 0.5^n,$$ where $\varepsilon$ is taken from Table~\ref{Table:used-constants}. The simulations were run for each $\varepsilon_n$ and corresponding $\lambda_D$ value
and maximum number of degrees of freedom and cumulative CPU time were recorded.
The simulation time $t$ for each $\lambda_D$ was chosen to be $\tau$ --- the
characteristic time scale --- and each simulation
was divided equally into fifteen time steps. No PID controller was used.
